\documentclass[letter,11pt]{article}
\usepackage{Loader}
\begin{document}

% ====================
% EXPERIENCE A
% ====================
\subsection{{Senior Research (Team) Project \hfill JAN 2022 --- MAY 2022}}
\subtext{Georgia State University \hfill Atlanta, GA}
\begin{zitemize}
\item Developed deep learning algorithms that recover differential equations 
    from simulated physcial systems.
\item Reproduced existing results from the "Sparse Identification of Nonlinear Dynamics (SINDy)" research paper by Brunton et al.
\item Independently developed data generation, visualization, and debugging tools to support algorithm develpment team and automate repetitive tasks. 
\item Implemented custom PyTorch Autoencoder to recover equations from transformed data and high dimensional embeddings.
\item Leveraged Agile methodologies and Trello for project management to effectively meet deadlines and enhance team collaboration. 
\end{zitemize}
% ====================
% EXPERIENCE B

\subsection{{Software Engineering Intern \hfill SEPT 2019 --- JAN 2020}}
\subtext{IDLogiq \hfill Santa Clara, Ca (Remote)}
\begin{zitemize}
\item Participated in technical discussions focusing on system design and application architecture.
\item Engaged with a diverse tech stack including Node, React, Typescript, Docker, Kubernetes, MongoDB, Meteor JS, and Cordova.
\item Discussed system design tradeoffs such as Publish/Subscribe architecture and web socket technology.
\item Assisted marketing team in designing promotional materials using Adobe Illustrator and Figma.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Tutor - CS, Math, Physics \hfill JAN 2019 --- DEC 2019}}
\subtext{Self-employed \hfill Alpharetta, GA}
\begin{zitemize}
\item Tutored students in Computer Science, Math (up to differential equations) and Physics
\item Guided students to achieve their goals and enhance understanding of introductory programming, data structures, and Object-Oriented Programming (OOP) concepts.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
% \subsection{{Assistant Manager \hfill SEPT 2017 --- JAN 2020}}
% \subtext{ColdStone Cremery \hfill Lawrenceville, GA}
% \begin{zitemize}
% \item Developed a positive work environment consistently by treating all employees with respect and consideration.
% \item Worked with other managers to execute the proper division of work responsibilities among all employees of the store 
% \item Supervised crew members to optimize the work efficiency by strategically assigning them various tasks and managing day to day operations of the store 
% \end{zitemize}

\end{document}
