\documentclass[letter,11pt]{article}
\usepackage{Loader}

\begin{document}

%====================
% Project A
%====================
\subsection{{Modulo - Productivity App | C \hfill JULY 2023}}
\begin{zitemize}
\item Developed a terminal application allowing users to log end-of-day thoughts and review them the next morning.
\item Designed a robust time-slicing algorithm to sync application state with the users sleep schedule.
\item Created an interactive text-user-interface (TUI) editor using the ncurses library and an event-driven MVC architecture.
\item Used the cJSON library to serialize/deserialize user data to disk.
\end{zitemize}

%====================
% Project B
%====================
\subsection{{P2P File Tracker - Distributed File System | Python \hfill APRIL 2023}}
\begin{zitemize}
\item Developed a Peer-to-Peer (P2P) file tracker system for distributing and tracking file chunks across a network of peers.
\item Implemented client-side logic for checking in local chunks to the tracker and requesting missing chunks from other peers.
\item Engineered tracker-side logic to maintain a list of chunks and their locations, and respond to chunk location queries from clients.
\item Enabled customizable client setup with command-line arguments for directory usage, P2P transfer port, and client name.
\end{zitemize}

%====================
% Project C
%====================
\subsection{{Minimax Tic-Tac-Toe | React, TypeScript \hfill AUGUST 2021}}
\begin{zitemize}
\item Created an engaging Tic-Tac-Toe game using TypeScript, React, and CSS Flexbox.
\item Integrated an AI opponent utilizing the recursive Minimax algorithm ensuring that AI makes optimal moves.
\item Leveraged TypeScript's strong typing features to enhance the robustness of the application, significantly reducing potential bugs and ensuring code reliability.
\item Successfully deployed this application using the Netlify platform.
\end{zitemize}







%====================
% Project D
%====================
% \subsection{{Personal Website | JavaScript, React, Tailwind}}
% \begin{zitemize}
% \item created a personal portfolio using JavaScript, React framework, and Tailwind to learn more about front-end development  
% \end{zitemize}

\end{document}
